---
title: "Rio 2016 Olympics"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: 
      version: 4
      bootswatch: minty
runtime: shiny
resource_files:
- Rio-de-Janeiro-Olympic-Games-2016.webp
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(packcircles)
library(countrycode)
library(ggiraph)
library(plotly)
library(lubridate)
library(eeptools)
library(maps)
library(mapproj)
library(DT)

library(echarts4r.assets)
library(echarts4r)

library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(tm)

dat <- read_csv("Olympics_2016_Rio_Athletes.csv")

dat <- dat %>%
  mutate(country = case_when(
    nationality == 'IOA' ~ 'Independent Olympians',
    nationality == 'ISV' ~ 'United States Virgin Islands',
    nationality == 'LIB' ~ 'Lebanon',
    nationality == 'ROT' ~ 'Refugee Olympic Team',
    nationality == 'SIN' ~ 'Singapore',
    nationality >0 ~ countrycode(nationality, "ioc", "country.name"))) %>%
  mutate(continent = case_when(
    nationality == 'IOA' ~ 'Independent',
    nationality == 'ISV' ~ 'Americas',
    nationality == 'LIB' ~ 'Asia',
    nationality == 'ROT' ~ 'Independent',
    nationality == 'SIN' ~ 'Asia',
    nationality == 'KOS' ~ 'Europe',
    nationality >0 ~ countrycode(nationality, "ioc", "continent"))) %>%
  mutate(continent_id = case_when(
    continent == 'Americas' ~ 1,
    continent == 'Europe' ~ 2,
    continent == 'Asia' ~ 3,
    continent == 'Africa' ~ 4,
    continent == 'Oceania' ~ 5,
    continent ==  'Independent' ~ 6)) %>%
  mutate(total = gold + silver + bronze) %>%
  mutate(dob = mdy(dob))

cent <- function(x, year=1940){
  m <- year(x) %% 100
  year(x) <- ifelse(m > year %% 100, 1900+m, 2000+m)
  x
}

dob2 = as.tibble(cent(dat$dob)) %>%
  rename("dob2"="value")

dat <- add_column(dat, as.vector(dob2)) %>%
  mutate(age = floor(interval(start=dob,
                              end=ymd("2016-08-05")) / 
                       duration(n=1, unit="years")))

```

Introduction {data-orientation=rows}
======================================

### 2016 Rio de Janeiro Olympic Games animated medals race

<style>
.shiny-app-frame {
  position: fixed;
  left: 0;
  top: 50px;
  bottom: 0;
  right: 0;
}
.shiny-app-frame iframe {
  width: 100%;
  height: 100%;
  border: none;
}
</style>

<div class="shiny-app-frame"> 
  <iframe src='https://flo.uri.sh/visualisation/15922977/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%; height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'>
  </iframe>
  <div style='width:100%!;margin-top:4px!important;text-align:right!important;'>
    <a class='flourish-credit'
    href='https://public.flourish.studio/visualisation/15922977/?utm_source=embed&utm_campaign=visualisation/15922977' target='_top' style='text-decoration:none!important'>
    </a>
  </div>
</div>

Row {}
-----------------------------------------------------------------------

### Contents

#### **The Athletes** explores the range of athletes that competed in the Rio 2016 Olympic Games, including global distribution, gender, continents and countries. For global distribution, click and drag the map to zoom in on the region, and double-click to reset

<br>

#### **The Medalists** explores the medals and medalists of the Games. Configure the medals, nationality & sport input parameters on the sidebar to filter the underlying data

<br>

#### **The Attributes** explores the attributes of medalists. What are observed common attributes of Olympic medalists? Configure sport & sex input parameters on the sidebar to filter the underlying data

### Logo

#### **Medals and Sport** shows a table of medal totals and two charts, one chart is the word cloud for the most competed sports and the other for the top ten most medals won countries. Please note that this section counts all individual medals awarded, whereas the official ranking tallies only 1 medal for a team placing in a sport

<br>

```{r}
library(knitr)
renderImage(
  list(src = "Rio-de-Janeiro-Olympic-Games-2016.webp",
       contentType = 'image/png',
       width = 300, height = 300,
       deleteFile=FALSE)
)
```

The Athletes {data-orientation=rows}
======================================

Row {data-height=500}
-----------------------------------------------------------------------

### Chart A

```{r, echo=FALSE, warning=FALSE}

world_map <- map_data("world") %>%
  rename("country"="region")

world_map <- world_map %>%
  mutate(nationality = countrycode(country, "country.name", "ioc"))

fig_dat_A <- dat %>%
  select(nationality, country)

temp_dat2 <- dat %>%
  select(country)

temp_dat2 <- as_tibble(table(temp_dat2)) %>% 
  rename("Athletes"="n")

fig_dat_A <- fig_dat_A %>%
  distinct(country, .keep_all = TRUE)

fig_dat_A <- inner_join(temp_dat2,
                        fig_dat_A,
                        by="country") %>%
  arrange(desc(Athletes))

dat2_combined <- left_join(world_map,
                           fig_dat_A,
                           by="nationality")

# Plot world map
gg2 <- ggplot() +
  geom_polygon(data=dat2_combined,
               mapping=aes(x=long,
                           y=lat,
                           group=group,
                           text = paste(country.x),
                           fill= Athletes, colour="gray10")) +
  scale_fill_distiller(palette=4,
                       direction=1) +
  scale_colour_manual(values = c("gray10")) +
  theme_bw() + 
  guides(color=FALSE) +
  coord_map(xlim=c(-180,180)) +
  labs(title="Global distribution of athletes", x="", y="") +
  theme(legend.position = c("right"),
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_blank(),
        plot.title = element_text(size=16, face="bold"))

ggplotly(gg2,tooltip=c("text", "fill")) %>% 
  hide_legend()

```

### Chart B

```{r, echo=FALSE}

fig_dat_B <- dat %>% 
  select(sex) 

fig_dat_B <- as_tibble(table(fig_dat_B)) %>%
  rename("count"="n") %>%
  mutate(per=round(count/sum(count) * 100)) %>%
  arrange(count)

gender<- data.frame(gender=fig_dat_B$sex, value=fig_dat_B$per,
                    path = c('path://M28.9624207,31.5315864 L24.4142575,16.4793596 C23.5227152,13.8063773 20.8817445,11.7111088 17.0107398,11.7111088 L12.112691,11.7111088 C8.24168636,11.7111088 5.60080331,13.8064652 4.70917331,16.4793596 L0.149791395,31.5315864 C-0.786976655,34.7595013 2.9373074,35.9147532 3.9192135,32.890727 L8.72689855,19.1296485 L9.2799493,19.1296485 C9.2799493,19.1296485 2.95992025,43.7750224 2.70031069,44.6924335 C2.56498417,45.1567684 2.74553639,45.4852068 3.24205501,45.4852068 L8.704461,45.4852068 L8.704461,61.6700801 C8.704461,64.9659872 13.625035,64.9659872 13.625035,61.6700801 L13.625035,45.360657 L15.5097899,45.360657 L15.4984835,61.6700801 C15.4984835,64.9659872 20.4191451,64.9659872 20.4191451,61.6700801 L20.4191451,45.4852068 L25.8814635,45.4852068 C26.3667633,45.4852068 26.5586219,45.1567684 26.4345142,44.6924335 C26.1636859,43.7750224 19.8436568,19.1296485 19.8436568,19.1296485 L20.3966199,19.1296485 L25.2043926,32.890727 C26.1862111,35.9147532 29.9105828,34.7595013 28.9625083,31.5315864 L28.9624207,31.5315864 Z M14.5617154,0 C17.4960397,0 19.8773132,2.3898427 19.8773132,5.33453001 C19.8773132,8.27930527 17.4960397,10.66906 14.5617154,10.66906 C11.6274788,10.66906 9.24611767,8.27930527 9.24611767,5.33453001 C9.24611767,2.3898427 11.6274788,0 14.5617154,0 L14.5617154,0 Z',
                             'path://M18.2629891,11.7131596 L6.8091608,11.7131596 C1.6685112,11.7131596 0,13.032145 0,18.6237673 L0,34.9928467 C0,38.1719847 4.28388932,38.1719847 4.28388932,34.9928467 L4.65591984,20.0216948 L5.74941883,20.0216948 L5.74941883,61.000787 C5.74941883,65.2508314 11.5891201,65.1268798 11.5891201,61.000787 L11.9611506,37.2137775 L13.1110872,37.2137775 L13.4831177,61.000787 C13.4831177,65.1268798 19.3114787,65.2508314 19.3114787,61.000787 L19.3114787,20.0216948 L20.4162301,20.0216948 L20.7882606,34.9928467 C20.7882606,38.1719847 25.0721499,38.1719847 25.0721499,34.9928467 L25.0721499,18.6237673 C25.0721499,13.032145 23.4038145,11.7131596 18.2629891,11.7131596 M12.5361629,1.11022302e-13 C15.4784742,1.11022302e-13 17.8684539,2.38997966 17.8684539,5.33237894 C17.8684539,8.27469031 15.4784742,10.66467 12.5361629,10.66467 C9.59376358,10.66467 7.20378392,8.27469031 7.20378392,5.33237894 C7.20378392,2.38997966 9.59376358,1.11022302e-13 12.5361629,1.11022302e-13'))

gender %>% 
  e_charts(gender) %>% 
  e_x_axis(splitLine=list(show = FALSE), 
           axisTick=list(show=FALSE),
           axisLine=list(show=FALSE),
           axisLabel= list(show=FALSE)) %>%
  e_y_axis(max=100, 
           splitLine=list(show = FALSE),
           axisTick=list(show=FALSE),
           axisLine=list(show=FALSE),
           axisLabel=list(show=FALSE)) %>%
  e_color(color= c("rgba(53, 136, 124, 0.8)", "'#eee'")) %>%
  e_pictorial(value, symbol = path, z=10, name= 'realValue', 
              symbolBoundingData= 100, symbolClip= TRUE) %>%
  e_pictorial(value, symbol = path, name= 'background', 
              symbolBoundingData= 100) %>% 
  e_labels(position = "bottom", offset= c(0, 10), 
           textStyle =list(fontSize= 20, fontFamily= 'Arial', 
                           fontWeight ='bold', 
                           color= "rgba(53, 136, 124, 0.8)"),
           formatter="{@[1]}% {@[0]}") %>%
  e_legend(show = FALSE) %>%
  e_title(text="Percentage of athletes by gender", textStyle.align='center') %>%
  e_theme("vintage") %>%
  e_toolbox_feature(feature = 'saveAsImage')

```

Row {data-height=500}
-----------------------------------------------------------------------

### Chart C

```{r, echo=FALSE, warning=FALSE}

fig_dat_C <- dat %>%
  select(nationality,
         country,
         continent,
         continent_id)

temp_dat1 <- dat %>%
  select(country)

temp_dat1 <- as_tibble(table(temp_dat1)) %>%
  rename("number_of_athletes"="n")
  
fig_dat_C <- fig_dat_C %>%
  distinct(country, .keep_all = TRUE)

fig_dat_C <- left_join(temp_dat1,
                       fig_dat_C,
                       by="country") %>%
  arrange(desc(number_of_athletes))

packing <- circleProgressiveLayout(fig_dat_C$number_of_athletes,
                                   sizetype='area')

fig_dat_C <- add_column(fig_dat_C,
                        packing)

dat.gg <- circleLayoutVertices(packing,
                               npoints=100)

continent_id <- rep(fig_dat_C$continent_id,
                    each=101)

dat.gg <- add_column(dat.gg,
                     continent_id)

number_of_athletes <- rep(fig_dat_C$number_of_athletes,
                          each=101)
dat.gg <- add_column(dat.gg,
                     number_of_athletes)

country <- rep(fig_dat_C$country,
               each=101)
dat.gg <- add_column(dat.gg,
                     country)

nationality <- rep(fig_dat_C$nationality,
                   each=101)
dat.gg <- add_column(dat.gg,
                     nationality)

if (requireNamespace("ggiraph")) {
  gg1 <- ggplot(data=dat.gg) + 
    ggiraph::geom_polygon_interactive(aes(x=x,
                                          y=y,
                                          group=id,
                                          fill=as.factor(continent_id),
                                          tooltip = c(paste0(country, " Athletes: \n",number_of_athletes)),
                                          data_id=x)) +
    scale_fill_manual(labels = c( "Americas",
                                  "Europe",
                                  "Asia",
                                  "Africa",
                                  "Oceania",
                                  "Independent"),
                      values=alpha(c(rgb(145, 100, 106,max=255),
                                     rgb(163, 212, 172,max=255),
                                     rgb(140, 141, 191,max=255),
                                     rgb(144, 204, 209,max=255),
                                     rgb(224, 151, 49,max=255),
                                     rgb(191, 189, 138,max=255)),
                                   0.75)) +
    geom_text(data=filter(fig_dat_C,
                          number_of_athletes > 100),
              aes(x=x, y=y,
                  size=number_of_athletes,
                  label=nationality),
              color="white") +
    scale_size(range = c(5, 9)) +
    guides(alpha=FALSE,
           size=FALSE,
           color = guide_legend(override.aes = list(alpha = 0.1)),
           fill=guide_legend(title="Region",override.aes = list(size=10))) +
    labs(title="Number of athletes by nationality & continent") +
    theme(legend.position = c("right"),
        legend.title = element_text(face = "bold",size=20),
        legend.text = element_text(size = 20),
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        plot.background=element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  face="bold",
                                  size=36)) +
    coord_equal()

 renderGirafe({ggiraph::ggiraph(ggobj = gg1,
                                width_svg = 20,
                                height_svg = 10)})
}

```

### Chart D

```{r, echo=FALSE, warning=FALSE}
#pie chart of gender, filter by country

fig_dat_D <- dat %>% 
  select(continent)

fig_dat_D <- as_tibble(table(fig_dat_D)) %>%
  rename("count"="n") %>%
  mutate(per=count/sum(count)) %>%
  arrange(count)

plot_ly(fig_dat_D,
        labels = ~continent,
        values = ~per,
        type = 'pie',
        textinfo = 'label+percent',
        insidetextfont = list(size = 24),
        hoverinfo = 'text',
        text = ~paste(continent, "athletes:", count),
        marker = list(colors = c("rgba(191, 189, 138, 1)",
                                 "rgba(224, 151, 49, 1)",
                                 "rgba(144, 204, 209, 1)",
                                 "rgba(140, 141, 191, 1)",
                                 "rgba(145, 100, 106, 1)",
                                 "rgba(163, 212, 172, 1)"),
                      line = list(color = '#000000', width = 2))) %>%
  
  layout(title = "<b>Percentage of athletes by continents<b>",
         font=list(size = 12),
         legend=list(title=list(text='<b>Continent</b>')))

```

The Medalists {data-orientation=rows}
======================================

Input Parameters {.sidebar}
-----------------------------------------------------------------------

### Filter

```{r}
sidebar_dat1 <- dat %>%
  filter(total > 0)

selectInput(inputId="my_medal",
            label="medal",
            choices=c("total","gold","silver","bronze"),
            multiple=FALSE,
            selected="total")

selectInput(inputId="my_nationality",
            label="nationality",
            choices=sort(unique(sidebar_dat1$nationality)),
            multiple=TRUE,
            selected=unique(sidebar_dat1$nationality))

selectInput(inputId="my_sport",
            label="sport",
            choices=sort(unique(sidebar_dat1$sport)),
            multiple=TRUE,
            selected=unique(sidebar_dat1$sport))

```


Row {data-height=500}
-----------------------------------------------------------------------

### Chart E

```{r, echo=FALSE}

renderPlotly({
  fig_dat_E <- dat %>%
    select(nationality,sport,gold,silver,bronze,total) %>%
    filter(nationality %in% input$my_nationality) %>%
    filter(sport %in% input$my_sport) %>%
    group_by(sport) %>%
    mutate(count = n())
  
  fig_dat_E <- aggregate(cbind(gold,silver,bronze,total) ~ sport,
                         data = fig_dat_E,
                         FUN = sum,
                         na.rm = TRUE) %>%
    arrange(desc(total)) %>%
    pivot_longer(cols=c(gold,silver,bronze),
                 names_to="medal",
                 values_to="count")
  
  fig_dat_E <- fig_dat_E[1:30, ]
  
  fig_dat_E$medal <- factor(fig_dat_E$medal,
                            levels = c("gold", "silver", "bronze"))
  
  if(input$my_medal != "total"){
    fig_dat_E <- fig_dat_E %>%
      filter(medal == input$my_medal)
 } 

if(input$my_medal == "gold"){
  my_fill <- c(alpha("gold"))
} else if(input$my_medal == "silver"){
  my_fill <- c(alpha("grey"))
} else if(input$my_medal == "bronze"){
  my_fill <- c(alpha(rgb(0.804,0.498,0.196)))
} else {
  my_fill <- c(alpha("gold"),alpha("grey"),alpha(rgb(0.804,0.498,0.196)))
}

gg6 <- ggplot(fig_dat_E,
              aes(x=reorder(sport,-count),
                  y=count,
                  fill= medal,
                  text = paste(count, medal,"medalists"),
                  color="gray50")) +
  geom_bar(stat="identity") +
  labs(x="Sport", y="Medals",
       title="<b>Top 10 most awarded sports<b>") +
  scale_fill_manual(values=my_fill) +
  scale_colour_manual(values = c("gray50"),
                      name="") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(size=.1,
                                          color="darkgrey"),
        axis.text.x = element_text(size=6))

ggplotly(gg6, tooltip=c("text")) %>% 
  hide_legend()
})

```

Row {data-height=400}
-----------------------------------------------------------------------

### Chart F

```{r, echo=FALSE}

renderGirafe({
  fig_dat_F <- dat %>%
    select(nationality,
           sport,
           country,
           sex,!!as.symbol(input$my_medal)) %>%
    rename("medal"=input$my_medal) %>%
    filter(nationality %in% input$my_nationality) %>%
    filter(sport %in% input$my_sport) %>%
    group_by(country,sex) %>%
    mutate(count = n())

fig_dat_F <- aggregate(cbind(medal) ~ country + sex + nationality,
                      data = fig_dat_F, FUN = sum, na.rm = TRUE) %>%
  #need to filter to remove zeros for x & y of dat.gg
  filter(medal >0 ) %>% 
  arrange(country)

packing <- circleProgressiveLayout(fig_dat_F$medal,
                                   sizetype='area')

fig_dat_F <- add_column(fig_dat_F,
                       packing)

dat.gg <- circleLayoutVertices(packing,
                               npoints=100)

sex <- rep(fig_dat_F$sex,
           each=101)
dat.gg <- add_column(dat.gg,
                     sex)

medal <- rep(fig_dat_F$medal,
             each=101)
dat.gg <- add_column(dat.gg,
                     medal)

country <- rep(fig_dat_F$country,
               each=101)
dat.gg <- add_column(dat.gg,
                     country)

nationality <- rep(fig_dat_F$nationality,
                   each=101)
dat.gg <- add_column(dat.gg,
                     nationality)

max(dat.gg$medal,
    na.rm = TRUE)

if(max(dat.gg$medal, na.rm = TRUE) <= 5){
  display_filter <- 0
} else if(max(dat.gg$medal, na.rm = TRUE) <= 10){
  display_filter <- 5
} else if(max(dat.gg$medal, na.rm = TRUE) <= 15){
  display_filter <- 10
} else {
  display_filter <- 15
}

if (requireNamespace("ggiraph")) {
  gg4 <- ggplot(data=dat.gg) +
      ggiraph::geom_polygon_interactive(
        aes(x=x, y=y,
            group=id,
            fill=as.factor(sex),
            tooltip = c(paste0(country, " ",
                               sex, " ",
                               input$my_medal, " Medalists: \n",medal)),
            data_id=x)) +
    scale_fill_manual(labels = c("Female",
                                 "Male"),
                      values=alpha(c(rgb(163, 212, 172,max=255),
                                     rgb(140, 141, 191,max=255)),0.75)) +
    geom_text(data=filter(fig_dat_F,
                          medal > display_filter),
              aes(x=x, y=y,
                  size=medal,
                  label=nationality),
              color="white") +
    scale_size(range = c(5,9)) +
    guides(alpha=FALSE,
           size=FALSE,
           color = guide_legend(override.aes = list(alpha = 0.1)),
           fill=guide_legend(title="Gender")) +
    labs(title="Medals by nationality and gender") +
    theme(legend.position = c("right"),
          legend.title = element_text(face = "bold",size=22),
          legend.text = element_text(size = 22),
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_blank(),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          plot.background=element_blank(),
          plot.title = element_text(hjust = 0.5,
                                    size=36,
                                    face="bold")) + 
    coord_equal()
  ggiraph::ggiraph(ggobj = gg4,
                   width_svg = 16,
                   height_svg = 10,
                   width = 1)
  }
})

```

### Chart G

```{r, echo=FALSE}
#height vs weight, medals=size of points, facet gender?

renderPlotly({
  gg5 <- (fig_dat_G <- dat %>%
            select(name,
                   nationality,
                   country,
                   sport,
                   sex,
                   height,
                   weight,!!as.symbol(input$my_medal)) %>%
            rename("medal"=input$my_medal) %>%
            filter(nationality %in% input$my_nationality) %>%
            filter(sport %in% input$my_sport) %>%
            filter(medal > 0) %>%
            ggplot(aes(x=weight,
                       y=height,
                       fill=sex,
                       size=medal,
                       text = paste("Name:", name,
                                    "\nGender:", sex,
                                    "\nCountry:", country,
                                    "\nHeight:", height,
                                    "m\nWeight:", weight,"kg\n",
                                    input$my_medal, "medals:", medal))) +
            geom_jitter() + 
            labs(title="<b> Medalists by height vs. weight and gender <b>",
                 x="Weight (kg)", y="Height (m)") +
            scale_fill_manual(values=alpha(c(rgb(163, 212, 172,max=255),
                                             rgb(140, 141, 191,max=255)),
                                           0.5),
                              name="")) +
    scale_size_continuous(range=c(3,10),
                          name="") +
    theme_light() +
    ylim(1.4,2.2) +
    xlim(30,160)

ggplotly(gg5,
         tooltip=c("text")) %>%
  layout(legend = list(title = list(text = "<b>Gender</b>")))
})
  
```

The Attributes {data-orientation=rows}
======================================

Input Parameters {.sidebar}
-----------------------------------------------------------------------

### Filter

```{r}

sidebar_dat2 <- dat %>%
  filter(total > 0)

selectInput(inputId="my_sex",
            label="gender",
            choices=c("female","male"),
            multiple=TRUE,
            selected=c("female","male"))

selectInput(inputId="my_sport2",
            label="sport",
            choices=sort(unique(sidebar_dat2$sport)),
            multiple=TRUE,
            selected=unique(sidebar_dat2$sport))

```

Row {data-height=500}
-----------------------------------------------------------------------

### Chart H

```{r, echo=FALSE}

renderPlotly({
  
fig_dat_H <- dat %>% 
  select(sex, sport, weight, height, age, total) %>%
  filter(sex %in% input$my_sex) %>%
  filter(sport %in% input$my_sport2) %>%
  rename("weight_kg"="weight") %>% 
  rename("height_m"="height") %>%
  rename("age_years"="age")

fig_dat_H <- fig_dat_H %>%
  pivot_longer(cols=c(weight_kg,
                      height_m,
                      age_years),
               names_to="variable",
               values_to="metric")

fig_dat_H <- aggregate(total ~ metric + variable,
                       data = fig_dat_H,
                       FUN = sum,
                       na.rm = TRUE) 

fig_dat_H$variable <- factor(fig_dat_H$variable,
                             levels = c("weight_kg", "height_m", "age_years"))

gg7 <- ggplot(fig_dat_H,
              aes(x=metric,
                  y=total,
                  fill=variable,
                  color="black",
                  group=1,
                  text=paste0(variable, ": ",
                              metric, "\nmedalists: ", total))) +
    geom_area() +
  geom_point(aes(x=metric, y=total)) +
    labs(title="<b> Distribution of medalists by weight, height, age <b>",x="",y="Medals") +
    facet_wrap(~variable,scales = "free") +
    scale_colour_manual(values = c("black"),name="") +
    scale_fill_manual(values = c(rgb(255,187,120,max=255),
                                 rgb(152,223,138,max=255),
                                 rgb(174,199,232,max=255))) +
  theme_light() + 
  theme(plot.title = element_text(size=20,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        strip.background = element_rect(color = "black", size = 1))

ggplotly(gg7, tooltip=c("text")) %>% 
  hide_legend() %>%
  layout(margin=list(t = 100))
})

```

Row {data-height=500}
-----------------------------------------------------------------------

### Chart I

```{r, echo=FALSE}

renderPlotly({
  fig_dat_I <- dat %>% 
    select(sex, sport, weight, height, age, total) %>%
    filter(sex %in% input$my_sex) %>%
    filter(sport %in% input$my_sport2) %>%
    filter(total > 0) %>%
    rename("weight_kg"="weight") %>% 
    rename("height_m"="height") %>%
    rename("age_years"="age")

fig_dat_I <- fig_dat_I %>%
  pivot_longer(cols=c(weight_kg, height_m, age_years),
               names_to="variable",
               values_to="metric")

fig_dat_I$variable <- factor(fig_dat_I$variable,
                             levels = c("weight_kg",
                                        "height_m",
                                        "age_years"))

gg8 <- ggplot(fig_dat_I,
              aes(x=as.factor(variable),
                  y=metric,
                  fill=variable)) +
  geom_boxplot() +
  facet_wrap(~variable,
             scales = "free") +
  labs(title="<b> Spread of medalists by weight, height, age <b>",
       x="", y="") + 
  scale_fill_manual(values = c(rgb(255,187,120,max=255),
                               rgb(152,223,138,max=255),
                               rgb(174,199,232,max=255))) +
  theme_light() +
  theme(axis.text.x=element_blank(),
        plot.title = element_text(size=20,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        strip.background = element_rect(color = "black", size = 1))

ggplotly(gg8) %>%
  hide_legend() %>%
  layout(margin=list(t = 100))
})

```

Medals and Sport {data-orientation=rows}
======================================

Row {data-height=500}
-----------------------------------------------------------------------
### Chart K

```{r}

fig_dat_K <- dat %>% 
  select(country, gold, silver, bronze, total)

fig_dat_K <- aggregate(cbind(gold,silver,bronze,total) ~ country,
                         data = fig_dat_K,
                         FUN = sum,
                         na.rm = TRUE)

fig_dat_K <- fig_dat_K[order(fig_dat_K$total,
                             fig_dat_K$gold,
                             fig_dat_K$bronze,
                             decreasing=TRUE),]

fig_dat_K <- fig_dat_K[1:10, ]

fig_dat_K %>% 
  e_charts(country) %>% 
  e_pictorial(total,
              symbol = ea_icons("medal"), 
              symbolRepeat = TRUE,
              z = -1,
              symbolSize = c(15, 15)) %>% 
  e_theme("vintage") %>%
  e_title("Top 10 countries by total medals won") %>% 
  e_flip_coords() %>%
  # Hide Legend
  e_legend(show = FALSE) %>%
  # Remove Gridlines
  e_x_axis(splitLine=list(show = TRUE)) %>%
  e_y_axis(splitLine=list(show = TRUE)) %>%
  # Format Label
  e_labels(fontSize = 16,
           fontWeight ='bold',
           position = "right",
           offset=c(10, 0))

```

### Chart L

```{r, echo=FALSE}
#Vector containing only text
fig_dat_L <- dat$sport

##create a corpus
olympicsSportCloud<-Corpus(VectorSource(fig_dat_L))

#create document term matrix
dtm <- TermDocumentMatrix(olympicsSportCloud)
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),
              decreasing=TRUE) 
Sportcloud_df <- data.frame(word = names(words),
                            freq=words)

#Generate word cloud
set.seed(1234) # for reproducibility
wordcloud(words = Sportcloud_df$word,
          freq = Sportcloud_df$freq,
          min.freq = 1,
          max.words=200,
          random.order=FALSE,
          rot.per=0.35,
          scale = c(3.5, 0.60),
          colors=brewer.pal(8, "Dark2"))

```

Row {}
-----------------------------------------------------------------------

### Medals Table

```{r}

renderDataTable({
  
  fig_dat <- dat %>%
    select(country, gold, silver, bronze, total)
  
  fig_dat <- aggregate(cbind(gold,silver,bronze,total) ~ country,
                       data = fig_dat,
                       FUN = sum,
                       na.rm = TRUE) %>%
    arrange(desc(total))
  
  fig_dat
  
})

```